\documentclass[9pt,letterpaper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[top=0.25in, bottom=0.25in, left=0.4in, right=0.4in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{array}

% Disable all paragraph indentation
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\pagestyle{empty}

% Section title formatting - clean underline style with better spacing
\titleformat{\section}
  {\vspace{0.5pt}\scshape\large\bfseries\raggedright}
  {}{0em}
  {}
  [\titlerule\vspace{0.5pt}]

% Adjust section top/bottom spacing for better breathing room
\titlespacing{\section}{0pt}{*0.8}{*0.6}

% Better spaced bullet points - improved from original but still compact
\setlist[itemize]{
  label=\textbullet,
  leftmargin=15pt,
  labelwidth=10pt,
  labelsep=5pt,
  itemsep=0pt,
  parsep=0pt,
  topsep=0pt,
  partopsep=0pt
}

% No link colors
\hypersetup{
  colorlinks=false,
  pdfborder={0 0 0}
}

\begin{document}

% Header with better spacing
\begin{center}
  {\LARGE\textbf{Matt McManus}}\\[4pt]
  \footnotesize
  610-348-3500 \textbar{} mattmcmanus41@gmail.com \textbar{} linkedin.com/in/mattmcm \textbar{} github.com/mmcmanus1\\[2pt]
  \textbf{Citizenship:} U.S Citizen \textbar{} \textbf{Location:} New York, NY
\end{center}

\vspace{4pt}

\section{Summary}
\small

ML Engineer leading AI/ML initiatives at Bridgewater Associates. Expert in LLMs, RL, and quantitative finance. Develops proprietary AI models for systematic investing and scalable infrastructure. Deploys ML systems managing \$150B+ AUM.

\vspace{3pt}

\section{Education}
\small

\textbf{Massachusetts Institute of Technology} \hfill Cambridge, MA\\[1pt]
\textit{Master of Engineering in Computer Science, GPA: 5.0/5.0} \hfill \textit{Aug. 2023 - Jun. 2024}
\begin{itemize}[topsep=0pt]
  \item Thesis: Navigation drift reduction using Scientific ML; Research: LLM macro forecasting, RL for LLMs
\end{itemize}

\vspace{0.5pt}

\textit{Bachelor of Science in Mathematics \& Computer Science} \hfill \textit{Sep. 2019 - Feb. 2024}
\begin{itemize}[topsep=0pt]
  \item Activities: MIT Varsity Squash, Phi Kappa Theta, MIT Pokerbots President, MIT Bitcoin Club, HKN Tutor
\end{itemize}

\vspace{3pt}

\section{Experience}
\small

\textbf{Bridgewater Associates} \hfill New York, NY\\[1pt]
\textit{ML Engineer / Research Scientist - AIA Labs} \hfill \textit{Sept. 2024 - Present}
\begin{itemize}[topsep=0pt]
  \item Lead development of proprietary AI models for macro-investing using \textbf{LLMs} and \textbf{RL} to generate alpha
  \item Built "no-peek" data-windowing pipeline keyed to news\_end\_date, speeding thematic analysis \textbf{4x}
  \item Developing transformer now-casting models blending alt-data with market signals; cut GDP-RMSE \textbf{15\%}
  \item Build quantitative research infrastructure for \textbf{factor discovery} and \textbf{regime detection}, processing petabytes of data for \textbf{\$150B+ AUM}
  \item Collaborate with Daniel Kang to benchmark internal temporal search system for systematic investing
\end{itemize}

\vspace{0.5pt}

\textit{Investment Engineer Intern} \hfill \textit{Jun. 2023 - Aug. 2023}
\begin{itemize}[topsep=0pt]
  \item Developed quantitative models for systematic investment strategies using \textbf{Python/Julia}, improving Sharpe ratio by \textbf{15\%} and reducing drawdown by \textbf{20\%}
  \item Research on alternative data and \textbf{NLP} sentiment analysis, generating \textbf{3} alpha signals with IR > \textbf{0.8}
  \item Built portfolio optimization algorithms and backtesting frameworks for multi-asset strategies
\end{itemize}

\vspace{0.5pt}

\textbf{Two Sigma} \hfill New York, NY\\[1pt]
\textit{Quantitative Research (Part-time)} \hfill \textit{Jan. 2023 - Jun. 2024}
\begin{itemize}[topsep=0pt]
  \item Conducted fast-cycle experiments on \textbf{factor discovery} and \textbf{regime detection} for systematic trading
  \item Developed ML models for alternative data analysis and signal generation, improving alpha decay by \textbf{30\%}
  \item Researched high-frequency market microstructure patterns for alpha generation
\end{itemize}

\vspace{0.5pt}

\textbf{MIT Julia Lab} \hfill Cambridge, MA\\[1pt]
\textit{Research Assistant} \hfill \textit{Sep. 2022 - May 2024}
\begin{itemize}[topsep=0pt]
  \item Developed physics-informed \textbf{neural-ODE} framework reducing navigation drift by \textbf{60\%} in GPS-denied environments
  \item Collaborated with aerospace industry partners on real-world deployment and validation
\end{itemize}

\vspace{0.5pt}

\textbf{Delphi Digital} \hfill New York, NY\\[1pt]
\textit{Quantitative Analyst} \hfill \textit{May 2022 - Aug. 2022}
\begin{itemize}[topsep=0pt]
  \item Created risk framework for new DeFi protocol, analyzing statistical and \textbf{ML techniques} for quantitative risk assessment
  \item Conducted quantitative analysis of crypto markets and DeFi protocols using \textbf{Python/SQL}
\end{itemize}


\vspace{4pt}

\section{Projects \& Research}
\small

\textbf{Scientific ML for INS:} Developed neural-ODE methodology reducing navigation drift by \textbf{60\%} using physics-informed ML\\[1pt]
\textbf{Multi-Agent RL:} Built cyber security simulator for agents learning via \textbf{reinforcement learning} and implicit communication\\[1pt]
\textbf{Deep Network Interpolation:} Created novel algorithm outperforming current models for low-complexity DNN solutions\\[1pt]
\textbf{LLM Macro Forecasting:} Applied LLMs to economic forecasting, achieving \textbf{25\%} improvement in prediction accuracy

\vspace{4pt}

\section{Technical Skills}
\small

\textbf{Programming:} Python, Julia, C++, Scala, Java, Go, SQL/Spark, JavaScript, R\\[1pt]
\textbf{ML/AI:} PyTorch, TensorFlow, JAX, Hugging Face, Transformers, Reinforcement Learning, Scientific ML, XGBoost\\[1pt]
\textbf{Infrastructure:} AWS, Docker, Kubernetes, Git, CI/CD, MLflow, Spark, Redis, PostgreSQL\\[1pt]
\textbf{Finance:} Quantitative Research, Factor Models, Backtesting, Risk Management, Market Microstructure

\vspace{4pt}

\section{Leadership \& Achievements}
\small

\textbf{MIT Pokerbots President:} Led 7-person team running AI poker competition for \textbf{250+} students, secured \textbf{\$100k+} sponsorships\\[1pt]
\textbf{MIT Varsity Squash:} Achieved National Team Ranking of \textbf{16th} in U.S. (2023-2024), 4-year starter\\[1pt]
\textbf{Publications:} Evaluating GPT-3 Performance in Cybersecurity Scenarios - Computers \& Security Journal\\[1pt]
\textbf{Honors:} MIT Pokerbots 1st Place, HackMIT Award Winner, Summa Cum Laude

\vfill
\end{document}