\documentclass[10pt,letterpaper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[top=0.25in, bottom=0.25in, left=0.4in, right=0.4in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{array}

% Disable all paragraph indentation
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\pagestyle{empty}

% Section title formatting - ultra clean with perfect proportions
\titleformat{\section}
  {\vspace{2pt}\scshape\large\bfseries\raggedright}
  {}{0em}
  {}
  [\titlerule\vspace{0.5pt}]

% Optimized section spacing for ultra-clean aesthetic
\titlespacing{\section}{0pt}{*1.0}{*0.8}

% Perfectly aligned bullet points with optimal spacing
\setlist[itemize]{
  label=\textbullet,
  leftmargin=15pt,
  labelwidth=10pt,
  labelsep=5pt,
  itemsep=1pt,
  parsep=0pt,
  topsep=1pt,
  partopsep=0pt
}

% Clean hyperlink styling
\hypersetup{
  colorlinks=false,
  pdfborder={0 0 0}
}

\begin{document}

% Header with refined spacing and typography
\begin{center}
  {\LARGE\textbf{Matt McManus}}\\[4pt]
  \footnotesize
  610-348-3500 \textbar{} mattmcmanus41@gmail.com \textbar{} linkedin.com/in/mattmcm \textbar{} github.com/mmcmanus1\\[1pt]
  \textbf{Citizenship:} U.S Citizen \textbar{} \textbf{Location:} New York, NY
\end{center}

\vspace{4pt}

\section{Summary}
\small
ML Engineer with proven experience leading AI/ML initiatives at Bridgewater Associates. Deep expertise in large language models, reinforcement learning, and quantitative finance. Skilled at developing proprietary AI models for systematic investment strategies and building scalable infrastructure. Adept at deploying ML systems managing \$150B+ AUM through innovative research and robust model development.

\vspace{2pt}

\section{Education}
\small
\textbf{Massachusetts Institute of Technology} \hfill Cambridge, MA\\[0.5pt]
\textit{Master of Engineering in Computer Science, GPA: 5.0/5.0} \hfill \textit{Aug. 2023 - Jun. 2024}
\begin{itemize}
  \item Thesis: Inertial Navigation System Drift Reduction Using Scientific Machine Learning
  \item Research: LLM-Driven Macro Forecasting, Reinforcement Learning for LLMs, Scientific ML
\end{itemize}

\vspace{0.5pt}

\textit{Bachelor of Science in Computer Science} \hfill \textit{Sep. 2019 - Feb. 2024}
\begin{itemize}
  \item Activities: MIT Varsity Squash, Phi Kappa Theta, MIT Pokerbots President, MIT Bitcoin Club, HKN Tutor
\end{itemize}

\vspace{2pt}

\section{Experience}
\small
\textbf{Bridgewater Associates} \hfill New York, NY\\[0.5pt]
\textit{ML Engineer / Research Scientist - AIA Labs} \hfill \textit{Sept. 2024 - Present}
\begin{itemize}
  \item Lead development of proprietary AI models for macro-investing, leveraging \textbf{LLMs} and \textbf{reinforcement learning}
  \item Built "no-peek" data-windowing pipeline keyed to news\_end\_date, speeding thematic analysis \textbf{4x}
  \item Developing transformer now-casting models blending alt-data with market signals; cut GDP-RMSE \textbf{15\%}
  \item Collaborate with Daniel Kang to benchmark internal temporal search system for \textbf{\$150B+ AUM}
\end{itemize}

\vspace{0.5pt}

\textit{Investment Engineer Intern} \hfill \textit{Jun. 2023 - Aug. 2023}
\begin{itemize}
  \item Developed quantitative models for systematic investment strategies using \textbf{Python} and \textbf{Julia}, improving portfolio Sharpe ratio by \textbf{15\%} and reducing maximum drawdown by \textbf{20\%}
  \item Conducted research on alternative data sources including \textbf{NLP} sentiment analysis, generating \textbf{3} new alpha signals with information ratios exceeding \textbf{0.8}
\end{itemize}

\vspace{1pt}

\textbf{Two Sigma} \hfill New York, NY\\[0.5pt]
\textit{Quantitative Research (Part-time)} \hfill \textit{Jan. 2023 - Jun. 2024}
\begin{itemize}
  \item Conducted fast-cycle experiments on \textbf{factor discovery} and \textbf{regime detection} for systematic trading
  \item Developed ML models for alternative data analysis and signal generation, improving alpha decay by \textbf{30\%}
\end{itemize}

\vspace{1pt}

\textbf{MIT Julia Lab} \hfill Cambridge, MA\\[0.5pt]
\textit{Research Assistant} \hfill \textit{Sep. 2022 - May 2024}
\begin{itemize}
  \item Developed physics-informed \textbf{neural-ODE} framework reducing navigation drift by \textbf{60\%} in GPS-denied environments
\end{itemize}

\vspace{1pt}

\textbf{Delphi Digital} \hfill Cambridge, MA\\[0.5pt]
\textit{Quantitative Analyst} \hfill \textit{May 2022 - Aug. 2022}
\begin{itemize}
  \item Created risk framework for new DeFi protocol, analyzing statistical and \textbf{ML techniques} for quantitative risk assessment
  \item Researched methods to optimize decentralized finance risk parameters using \textbf{Python} and data analysis
\end{itemize}


\vspace{2pt}

\section{Projects \& Research}
\small
\textbf{Scientific ML for INS} - Developed neural-ODE methodology reducing navigation drift by \textbf{60\%} using physics-informed ML\\[0.5pt]
\textbf{Multi-Agent RL} - Built cyber security simulator for agents learning via \textbf{reinforcement learning} and implicit communication\\[0.5pt]
\textbf{Deep Network Interpolation} - Created novel algorithm outperforming current models for low-complexity DNN solutions

\vspace{2pt}

\section{Technical Skills}
\small
\textbf{Programming:} Python, Julia, C++, Scala, Java, Go, SQL/Spark, JavaScript, R\\[0.5pt]
\textbf{ML/AI:} PyTorch, TensorFlow, JAX, Hugging Face, Transformers, Reinforcement Learning, Scientific ML, XGBoost\\[0.5pt]
\textbf{Infrastructure:} AWS, Docker, Kubernetes, Git, CI/CD, MLflow, Spark, Redis, PostgreSQL\\[0.5pt]
\textbf{Finance:} Quantitative Research, Factor Models, Backtesting, Risk Management, Market Microstructure

\vspace{2pt}

\section{Leadership \& Achievements}
\small
\textbf{MIT Pokerbots President:} Led 7-person team running AI poker competition for \textbf{250+} students, secured \textbf{\$100k+} sponsorships\\[0.5pt]
\textbf{MIT Varsity Squash:} Achieved National Team Ranking of \textbf{16th} in U.S. (2023-2024), 4-year starter\\[0.5pt]
\textbf{Publications:} Evaluating GPT-3 Performance in Cybersecurity Scenarios - Computers \& Security Journal\\[0.5pt]
\textbf{Honors:} MIT Pokerbots 1st Place, HackMIT Award Winner, Summa Cum Laude

\end{document}