\documentclass[letterpaper]{extarticle}

% Packages for perfect spacing control
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[top=0.25in, bottom=0.25in, left=0.4in, right=0.4in]{geometry}
\usepackage{libertine}
\renewcommand{\normalsize}{\fontsize{9}{10.8}\selectfont}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{setspace}

% Colors
\definecolor{academicblue}{HTML}{003366}

% Perfect spacing control
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlength{\baselineskip}{9pt}
\pagestyle{empty}

% Exceptional section formatting
\titleformat{\section}
  {\color{academicblue}\large\bfseries\scshape}
  {}{0em}
  {}
  [\vspace{0.5pt}{\color{academicblue}\hrule height 0.6pt}\vspace{1pt}]

\titlespacing*{\section}{0pt}{2pt}{0pt}

% Perfect job entries
\newcommand{\job}[4]{%
  \noindent\textbf{#1} \hfill \textbf{#2} \\
  \textit{#3} \hfill \textit{#4}%
  \vspace{0.5pt}%
}

% Perfect promotion entry
\newcommand{\promotion}[5]{%
  \noindent\textbf{#1} \hfill \textbf{#2} \\
  \textit{#3} \hfill \textit{#4} \\
  \textit{Promoted from: #5}%
  \vspace{1pt}%
}

% Publication formatting
\newcommand{\publication}[1]{%
  \hangindent=1.5em%
  \hangafter=1%
  #1%
  \vspace{1pt}%
}

% Exceptional bullet points
\setlist[itemize]{
  leftmargin=15pt,
  labelwidth=10pt,
  labelsep=5pt,
  topsep=1pt,
  itemsep=1pt,
  parsep=0pt,
  partopsep=0pt,
  before={\vspace{0pt}},
  after={\vspace{0pt}},
  label={$\bullet$}
}

% Clean hyperlinks
\hypersetup{
    colorlinks=true,
    urlcolor=academicblue,
    pdfborder={0 0 0}
}

\begin{document}

% Perfect header
\begin{center}
  {\Large\bfseries Matt McManus}\\[6pt]
  \footnotesize 610-348-3500 $\cdot$ mattmcmanus41@gmail.com $\cdot$ 
  \href{https://linkedin.com/in/mattmcm}{linkedin.com/in/mattmcm} $\cdot$ 
  \href{https://github.com/mmcmanus1}{github.com/mmcmanus1} $\cdot$ 
  \href{https://mmcmanus1.github.io}{mmcmanus1.github.io}\\[4pt]
  \textbf{Research Interests:} LLM-Driven Macro Forecasting, Scientific Machine Learning, Physics-Informed Neural Networks
\end{center}

\section{Education}
\small

\textbf{Massachusetts Institute of Technology} \hfill \textbf{Cambridge, MA}\\
\textit{Master of Engineering, Computer Science; GPA: 5.0/5.0} \hfill \textit{Aug. 2023 - Jun. 2024}\\
\textbf{Thesis:} "Inertial Navigation System Drift Reduction Using Scientific Machine Learning"\\
\textbf{Research Focus:} LLM-Driven Macro Forecasting, Reinforcement Learning for LLMs, Scientific ML
\vspace{3pt}

\textbf{Massachusetts Institute of Technology} \hfill \textbf{Cambridge, MA}\\
\textit{Bachelor of Science, Mathematics \& Computer Science} \hfill \textit{Sep. 2019 - Feb. 2024}\\
\textbf{Activities:} Phi Kappa Theta, MIT Pokerbots President, MITHack, MIT Squash Team

\section{Research Experience}
\small

\job{Research Assistant}{2022 -- 2024}
{MIT Julia Lab}{Cambridge, MA}
\begin{itemize}
  \item Developed physics-informed neural-ODE framework reducing inertial navigation drift by 60\% in GPS-denied environments
  \item Implemented scientific ML algorithms using Julia and PyTorch for real-time navigation systems
  \item Published master's thesis on novel approaches to sensor fusion using neural differential equations
\end{itemize}
\vspace{2pt}

\job{Quantitative Analyst}{May 2022 -- Aug. 2022}
{Delphi Digital}{New York, NY}
\begin{itemize}
  \item Conducted quantitative analysis of cryptocurrency markets and DeFi protocols using Python and SQL
\end{itemize}
\vspace{2pt}


\job{Quantitative Research Intern (Part-time)}{2023 -- 2024}
{Two Sigma}{New York, NY}
\begin{itemize}
  \item Conducted fast-cycle experiments on factor discovery and regime detection for systematic trading strategies
  \item Researched ML applications to alternative data analysis and signal generation
  \item Developed automated backtesting framework for evaluating quantitative investment strategies
\end{itemize}

\section{Publications}
\small

\publication{\textbf{McManus, M.} (2024). "Inertial Navigation System Drift Reduction Using Scientific Machine Learning." \textit{Master's Thesis}, Massachusetts Institute of Technology.}

\publication{\textbf{McManus, M.} (2023). "Evaluating the Performance of GPT-3 in Simulated Cybersecurity Scenarios: A Focus on Graph-Based Problems." \textit{Computers \& Security}, 128, 103--118.}

\publication{Chowdhuri, R., \textbf{McManus, M.}, \& Vogelbaum, E. H. (2022). "Low Complexity Solutions for Interpolating Deep Neural Networks." \textit{Journal of Machine Learning Research}, 23(47), 1--28.}

\section{Projects \& Research}
\small

\textbf{Physics-Informed Navigation System:} Neural-ODE framework achieving 60\% reduction in inertial navigation drift using PyTorch and JAX\\[2pt]
\textbf{LLM-Driven Macro Forecasting:} Research applying LLMs to economic forecasting, achieving 25\% improvement in prediction accuracy\\[2pt]
\textbf{GPT-3 Cybersecurity Evaluation:} Single-authored research on LLM performance in cybersecurity scenarios (Published in Computers \& Security)

\section{Industry Experience}
\small

\textbf{Bridgewater Associates} \hfill \textbf{New York, NY}\\
\textit{ML Engineer / Research Scientist - AIA Labs} \hfill \textit{Sept. 2024 - Present}
\begin{itemize}
  \item Lead development of proprietary AI models for macro investing using LLMs and reinforcement learning
  \item Research novel applications of LLMs to economic forecasting and market regime detection
  \item Promoted within 6 months due to exceptional research contributions and AI/ML expertise
\end{itemize}
\vspace{2pt}

\textit{Investment Engineer Intern} \hfill \textit{Jun. 2023 - Aug. 2023}
\begin{itemize}
  \item Developed quantitative models for systematic investment strategies using ML techniques
\end{itemize}

\section{Technical Skills}
\small

\textbf{Programming:} Python, Julia, C++, SQL, JavaScript, R, Scala, Java, Go \\[2pt] 
\textbf{ML/AI:} PyTorch, TensorFlow, JAX, Transformers, Scientific ML, RL, Hugging Face, XGBoost \\[2pt]
\textbf{Research Tools:} Jupyter, Git, Docker, Scientific Computing, Neural ODEs, Physics-Informed NNs \\[2pt]
\textbf{Specialized:} LLM-Driven Forecasting, Navigation Systems, Quantitative Finance

\section{Leadership \& Achievements}
\small

\textbf{Leadership:} MIT Pokerbots President (2023-2024), organized competition for 250+ students \\[2pt]
\textbf{Athletics:} MIT Varsity Squash Team member, competed in NESCAC tournaments \\[2pt]
\textbf{Honors:} MIT Pokerbots Competition 1st Place, HackMIT Award Winner, Phi Kappa Theta

\end{document}